Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-09-19 pres/msr.tex
presentation mid update
presentation slides first draft

\begin{frame}
	\frametitle{Molten Salt Reactors}
		\textbf{Characteristics and challenges}
		\begin{itemize}
			\item Strong coupling between neutronics and thermal-hydraulics
			\begin{itemize}
				\item Strong Doppler and density feedback in the fuel salt
				\item Relatively more prompt response expected compared to
				existing LWRs
			\end{itemize}
			\item Movement and decay of delayed neutron precursors in the molten
			salt loop
			\begin{itemize}
				\item Conventional safety analysis codes do not account for the
				delayed neutron precursor movement
			\end{itemize}
			\item Constantly evolving fuel composition across the lifetime of an
			\gls{MSR}
			\begin{itemize}
				\item Reactor safety parameters and transient response may be
				different for \gls{BOL} vs \gls{EOL} fuel compositions
			\end{itemize}
		\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Molten Salt Reactors}
		\textbf{Characteristics and challenges}
		\begin{itemize}
			\item Strong coupling between neutronics and thermal-hydraulics
			\begin{itemize}
				\item Strong Doppler and density feedback in the fuel salt
				\item Relatively more prompt response expected compared to
				existing LWRs
			\end{itemize}
			\item Movement and decay of \gls{DNP} in the molten
			salt loop
			\begin{itemize}
				\item Conventional safety analysis codes do not account for the
				delayed neutron precursor movement
			\end{itemize}
			\item Constantly evolving fuel composition across the lifetime of an
			\gls{MSR}
			\begin{itemize}
				\item Reactor safety parameters and transient response may be
				different for start-up vs equilibrium fuel compositions
			\end{itemize}
		\end{itemize}
\end{frame}

### 2019-09-19 pres/neutron.tex
presentation slides first draft

\begin{frame}
	\frametitle{Neutronics Verification}
	\begin{columns}
		\column{5cm}
		\textbf{Moltres Simulation Details}
		\begin{itemize}
			\item Adaptive backward Euler time-stepper
			\item Six neutron groups, eight \gls{DNP} groups
			\item Vacuum neutron boundary condition on outer surfaces
			\item Uniform upward flow of 1.125 m s$^{-1}$
			\item Flow/decay of \glspl{DNP} and heat removal in the outer loop
			is simulated on a simplified 1D geometry separate from active core
			region
			\item Fixed heat removal rate to secondary loop system
		\end{itemize}
		\column{5cm}
		\begin{figure}
			\centering
			\includegraphics[width=.8\textwidth]{../paper/figures/mesh}
			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
			grey and red regions represent the fuel and blanket salt
			respectively.}
			\label{fig:mesh}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Results}
			\begin{figure}
				\centering
				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
				\caption{Fine-group and six-group neutron flux distributions
				from Serpent and Moltres (start-up composition without \gls{DNP}
				drift).}
				\label{fig:ntspec}
			\end{figure}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Neutronics Verification}
	\begin{columns}
		\column{5.5cm}
		\textbf{Moltres Simulation Details}
		\begin{itemize}
			\small
			\item Adaptive backward Euler time-stepper
			\item Six neutron groups, eight \gls{DNP} groups
			\item Vacuum neutron boundary condition on outer edges
			\item Uniform upward flow of 1.125 m s$^{-1}$
			\item Flow/decay of \glspl{DNP} and heat removal in the outer loop
			is simulated on a simplified 1D geometry separate from active core
			region
			\item Fixed heat removal rate to secondary loop system
		\end{itemize}
		\column{4.5cm}
		\begin{figure}
			\centering
			\includegraphics[width=.9\textwidth]{../paper/figures/mesh}
			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
			grey and red regions represent the fuel and blanket salt
			respectively.}
			\label{fig:mesh}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Results}
			\begin{figure}
				\centering
				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
				\caption{Fine-group and six-group neutron flux distributions
				from Serpent and Moltres (start-up composition without \gls{DNP}
				drift at 973 K).}
				\label{fig:ntspec}
			\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Temperature Reactivity Feedback}
			\begin{table}[t]
				\centering
				\caption{Temperature reactivity feedback coefficients.}
				\begin{tabular}{lccc}
					\hline
					\multirow{2}{*}{Composition} & {$\alpha_T$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm K$^{-1}$]} & Difference\\
					& Serpent & Moltres & [pcm K$^{-1}$]\\
					\hline
					Start-up & $-7.39 \pm 0.03$ & $-7.46$ & $-0.07$\\
					Early-life & $-7.25 \pm 0.03$ & $-7.33$ & $-0.08$\\
					Equilibrium & $-6.24 \pm 0.03$ & $-6.34$ & $-0.10$\\
					\hline
				\end{tabular}
				\label{table:reactivity}
			\end{table}	
\end{frame}
